---
title: "Hello, Tutorial!"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
```

This code computes the answer to one plus one, change it so it computes two plus two:

```{r addition, exercise=TRUE}
1 + 1
```
# pre-setup: can we prep an rstudio.cloud instance with certain things preloaded? (ggplot2, tidyverse, monty hall?)

# Actual workshop goes here!

## WHO AM I
## WHO ARE YOU

## Hello World
### What is R
### Why R
#### R vs. Python vs. Tableau vs. PowerBI vs. Julia (??)
### Python is better
### RStudio
### rstudio.cloud

### R Building Blocks
### Math stuff
### Loading packages
#### install.packages("tidyverse"), library(tidyverse)
### functions!
#### What is a function
#### Let's make a function
#### Data structures
##### How can I read data in R?
##### Basic data types
#### variables, integers, etc etc
#### vectors (example dice - die <- c(1:6))
#### Data frames
#### Subsetting data frames



## Dice Rolls
### How do we make a dice?
#### arbitrary sides
#### arbitrary rolls
#### writing a function for the roll (hopr 2.4)
#### do function initially without replace = TRUE, ask them what's wrong
### Weighting Dice Rolls
### Dataviz: Dice Rolls

## Monty Hall Problem

### THE TIDYVERSE
#### What is the tidyverse
#### Some tidyverse packages of note:
### ggplot2
### others

## CSVs
### Getting CSVs
### Cleaning unclean CSVs
### Dataviz: CSVs

## Playing with an example CSV
### something ALA related? wages? library school enrollment?

## ... ?
